\section{Introduction}

Todays software landscape is shaped by modern practices like continous integration. CI allows the production of more stable and less error-prone software by continously running tests specified by the user on the software. If any of those tests fails, the user gets notified and can inspect the failure using tools provided by the CI system. Continous Benchmarking tries to offer the same for software performance. The user specified tests get replaced by user specified benchmarks that are continously run on the software, giving the users insight of how the performance of their software changes over time. This is where PROJECTNAME comes into play. It offers the user an environment where he can easily keep track of the performance data and even inspect and compare the results by generating informative visualizations from them. 

\section{Goals}

\subsection{Required}

\criterium{Generation of \glspl{visualization} from benchmark data}
{crt:vis}
{For a given benchmark result, generate a \gls{visualization} and inspect it.}

\criterium{Comparison between different datapoints}
{crt:comp}
{For a given benchmark type, choose two (or more) datapoints (for example two different commits), and compare them by creating a visualization that shows the differences between the them.}

\criterium{Persistent storage of benchmark results}
{crt:storage}
{The system offers long term storage for benchmark results.}

\criterium{Overview about current state of benchmark performance}
{crt:overview}
{The system offers a overview that tells you the current performance for a given benchmarks and also whether it has improved or not.}


\subsection{Optional}

\criteriumOptional{Export and Sharing of \glspl{visualization}}
{crt:opt_export_share}
{Allows the download and the creation of a shareable link for a visualization.}

\criteriumOptional{Creation and use of \glspl{template}}
{crt:opt_templates}
{Allows the \gls{user} to create and use \glspl{template} for ease of use.}

\criteriumOptional{Tracking of benchmark performance}
{crt:opt_track}
{The system keeps track of the benchmark performance, notifying the \gls{user} in a predefined way if there are major changes.}


\subsection{Limitation}

\criteriumNot{\Gls{visualization} types are predefined}
{crt:limit_predefined}
{The \gls{visualization} types have to be predefined, otherwise the system would get too complex.}
