\section{Tests}

\test{Create Visualization}{tst:create-vis-single}
\tests{fnc:select}
\tests{fnc:configure}
\tests{fnc:display}
\tests{fnc:overview}

Tests the basic navigation of the webapp and the generation of a \gls{visualization} from a set of datapoints.

\teststep{User has the webapp open and no changes selected. The database contains benchmark data}
{User selects two changes}
{Changes get added to the list of selected changes}

\teststep{User has two changes selected}
{User selects the \enquote{Create New Plot} option}
{A popup with configuration options appears}

\teststep{User has two changes selected and the configuration popup open}
{User adjusts the configuration}
{Configuration gets updated on screen}

\teststep{User has two changes selected and the configuration popup open and has it configured}
{User selects the \enquote{Generate Plot} option}
{The \gls{visualization} matching the configuration gets displayed to the user}

\test{Post Benchmark Data}{tst:post-data}
\tests{fnc:storage}

Tests sending benchmark data to the system and storing it.

\teststepnostate{The system receives a POST request with valid data}
{The data gets stored in the database}

\test{Error Handling}{tst:error}
\tests{nfc:robust}

Tests the systemes ability to deal with malformed input data and invalid requests.

\teststep{Database is empty}
{System receives a POST request with malformed data for change A}
{System does not store the data}

\teststep{Database is empty}
{The webapp requests data for change A}
{An error message gets displayed on the webapp}

\test{Templates}{tst:template}
\tests{fnc:store-template}
\tests{fnc:load-template}

Tests the creation, storage and usage of templates.

\teststep{User has changes selected and the webapp with the configuration popup open. Configuration has been changed from the default.}
{User selects the \enquote{Save Template} option}
{Template gets stored in cookies.}

\teststep{Template is stored in cookies.}
{User selects the \enquote{Load Template} option}
{Template gets applied to the current configuration}

\test{Share}{tst:share}
\tests{fnc:share-link}

Tests the sharing of \glspl{visualization}.

\teststep{User has the webapp with a \gls{visualization} open}
{User selects the \enquote{Share} option}
{Link leads to a identical \gls{visualization}}

\test{Export}{tst:export}
\tests{fnc:export}

Tests the export of \glspl{visualization}.

\teststep{User has the webapp with a \gls{visualization} open}
{User selects the \enquote{Export} option}
{The \gls{visualization} gets downloaded}

\test{Performance Tracking}{tst:tracking}
\tests{fnc:calc}
\tests{fnc:track}
\tests{fnc:notify}

Tests the system ability to detect performance drops and notify external webservices.

\teststep{The database contains a change with high performance scores and a hook for an external webservice is set up}
{System gets a post request with data that has low performance scores}
{The external webserivce gets notified of the performance drop}
