\section{Tests}

\test{Create Plot}{tst:create-vis-single}
\tests{fnc:select}
\tests{fnc:configure}
\tests{fnc:display}
\tests{fnc:overview}

Tests the basic navigation of the web app and the generation of a \gls{plot} from a set of datapoints.

\teststep{User has the web app open and no commits selected. The database contains \glspl{benchmark result}}
{User selects two commits}
{Commits get added to the list of selected commits}

\teststep{User has two commits selected}
{User selects the \enquote{Create New Plot} option}
{A popup with configuration options appears}

\teststep{User has two commits selected and the configuration popup open}
{User adjusts the configuration}
{Configuration gets updated on screen}

\teststep{User has two commits selected and the configuration popup open and has it configured}
{User selects the \enquote{Generate Plot} option}
{The \gls{plot} matching the configuration gets displayed to the user}

\test{Post Benchmark Results}{tst:post-data}
\tests{fnc:storage}

Tests sending \glspl{benchmark result} to the system and storing it.

\teststepnostate{The system receives a POST request with valid data}
{The data gets stored in the database}

\test{Error Handling}{tst:error}
\tests{nfc:robust}

Tests the system's ability to deal with malformed input data and invalid requests.

\teststep{Database is empty}
{System receives a POST request with malformed data for commit A}
{System does not store the data}

\teststep{Database is empty}
{The web app requests data for commit A}
{An error message gets displayed on the web app}

\test{Templates}{tst:template}
\tests{fnc:store-template}
\tests{fnc:load-template}

Tests the creation, storage and usage of \glspl{template}.

\teststep{User has commits selected and the web app with the configuration popup open. Configuration has been changed from the default.}
{User selects the \enquote{Save Template} option}
{Template gets downloaded.}

\teststep{Template is downloaded.}
{User selects the \enquote{Load Template} option}
{Template gets applied to the current configuration}

\test{Share}{tst:share}
\tests{fnc:share-link}

Tests the sharing of \glspl{plot}.

\teststep{User has the web app with a \gls{plot} open}
{User selects the \enquote{Share} option}
{Link leads to an identical \gls{plot}}

\test{Export}{tst:export}
\tests{fnc:export}

Tests the export of \glspl{plot}.

\teststep{User has the web app with a \gls{plot} open}
{User selects the \enquote{Export} option}
{The \gls{plot} gets downloaded}

\test{Invalid Authentification}{tst:auth}
\tests{fnc:auth}

Tests the system's ability to reject data without valid authentification

\teststepnostate{The system receives a POST request with an invalid authentification}
{The system rejects the request and returns the corresponding error code}

\test{Performance Tracking}{tst:tracking}
\tests{fnc:calc}
\tests{fnc:track}
\tests{fnc:notify}

Tests the system's ability to detect performance drops and notify external webservices.

\teststep{The database contains a commit with high performance scores and a hook for an external webservice is set up}
{System gets a POST request with data that has low performance scores}
{The external webserivce gets notified of the performance drop}
